Vv caluclator

### 2023-02-16 code/analysis_code/vp.qmd
Plots for symposium

Data
```{r}
vp<- read_csv(file = here("data", "processed_data", "vp_clean_copies_date.csv")) #This file had dates manually added
sq <-read_csv(here("data", "raw_data", "vp_qPCR.csv")) #Manually replaced NaN with 0 for no amplifcation 
```
Standard Curve
```{r}
std<- sq %>%
  filter(
    Fluor %in% "HEX",
    Content %in% "Std")

std %>%
  ggplot() + geom_point(
    aes(x = log10(SQ),
        y = Cq))

>>>>

Data
```{r}
vp<- read_csv(file = here("data", "processed_data", "vp_clean_copies.csv")) #This file had dates manually added
#sq <-read_csv(here("data", "raw_data", "vp_qPCR.csv")) #Manually replaced NaN with 0 for no amplifcation 
```
Standard Curve
```{r}
#std<- sq %>%
  #filter(
    #Fluor %in% "HEX",
    #Content %in% "Std")
```

### 2023-02-16 code/wrangling_code/vv_copies_calclulator.qmd
Plots for symposium

Filter for HEX dye (samples). Cy5 is for IAC
```{r}
sq2<- sq %>% 
  select(filter_amt,SQ,Cq, Sample, Fluor, dilution) %>%
  filter(Fluor %in% "HEX")

redo2<- redo %>% 
  select(Cq, Sample, Fluor, Well) %>%
  filter(Fluor %in% "HEX",
         !Well %in% "K19")

@@

Cq --> Copies/mL
```{r}
copies<- filter %>%
   mutate(
   log_sq = ((Cq-36.497)/-3.166), #Equation of the line to get log(SQ)
    sq = 10^log_sq, #Unlog 
    copies_rxn = sq*15, #SQ*Reaction Volume
    copies_uL_1_10 = copies_rxn/1.2, #Copies/RXN / DNA Template Volume
    copies_uL_extract = copies_uL_1_10 *dilution, #(Copies/uL of 1:10)*(1 if there was no sample dilution // *10 if there was a 1:10 dilution etc.)
    concentration_factor = 100/filter_amt, #(Concentration factor = amount of eluted DNA from ZYMO) / (filter amount from vacuum filtration)
    copies_mL = copies_uL_extract*concentration_factor) %>%

@@

copies_redo<- filter_redo %>%
    mutate(
    log_sq = ((Cq-36.497)/-3.166), #Equation of the line to get log(SQ)
    sq = 10^log_sq, #Unlog 
    copies_rxn = sq*15, #SQ*Reaction Volume
    copies_uL_1_10 = copies_rxn/1.2, #Copies/RXN / DNA Template Volume
    copies_uL_extract = copies_uL_1_10 *dilution, #(Copies/uL of 1:10)*(1 if there was no sample dilution // *10 if there was a 1:10 dilution etc.)
    concentration_factor = 100/filter_amt, #(Concentration factor = amount of eluted DNA from ZYMO) / (filter amount from vacuum filtration)
    copies_mL = copies_uL_extract*concentration_factor) %>%

@@

>>>>

Filter for HEX dye (samples). Cy5 is for IAC
```{r}
sq2<- sq %>% 
  select(SQ,Cq, Sample, Fluor) %>%
  filter(Fluor %in% "HEX")

redo2<- redo %>% 
  select(Cq, Sample, Fluor, Well) %>%
  filter(Fluor %in% "HEX",
        !Well %in% "K19") #This triplicate amplified

@@

Cq --> Copies/mL
```{r}
copies<- filter %>%
   mutate(
   log_sq = ((Cq-37.606)/-3.409), #Equation of the line to get log(SQ). Equation is from Oyster STD Curve.
    sq = 10^log_sq, #Unlog 
    copies_rxn = sq*15, #SQ*Reaction Volume
    copies_uL_1_10 = copies_rxn/1.2, #Copies/RXN / DNA Template Volume
    copies_uL_extract = copies_uL_1_10 *dilution, #(Copies/uL of 1:10)*(1 if there was no sample dilution // *10 if there was a 1:10 dilution etc.)
    concentration_factor = 100/filter_amt, #(Concentration factor = amount of eluted DNA from ZYMO) / (filter amount from vacuum filtration)
    copies_mL = copies_uL_extract*concentration_factor) %>%

@@

copies_redo<- filter_redo %>%
    mutate(
    log_sq = ((Cq-37.606)/-3.409), #Equation of the line to get log(SQ). Equation is from Oyster STD CUrve.
    sq = 10^log_sq, #Unlog 
    copies_rxn = sq*15, #SQ*Reaction Volume
    copies_uL_1_10 = copies_rxn/1.2, #Copies/RXN / DNA Template Volume
    copies_uL_extract = copies_uL_1_10 *dilution, #(Copies/uL of 1:10)*(1 if there was no sample dilution // *10 if there was a 1:10 dilution etc.)
    concentration_factor = 100/filter_amt, #(Concentration factor = amount of eluted DNA from ZYMO) / (filter amount from vacuum filtration)
    copies_mL = copies_uL_extract*concentration_factor) %>%

@@

Cimpare Cq between OG and Redo
```{r}
#Deop NAs from +/- and lok at HEX
sq0<- sq %>%
  filter(
    !is.na(Sample),
    Fluor %in% "HEX")

redo0<- redo %>%
  filter(!is.na(Sample),
         Fluor %in% "HEX")

#copies0<- copies %>%
 # filter(!is.na(Sample))

#copies_redo0<- copies_redo %>%
 # filter(!is.na(Sample))

#Merge df
cq_comp<- 
  cbind(redo0, Cq_og= sq0$Cq) %>%
  #cbind(copies_redo0, copies_redo1 = sq0$copies_mL) %>%
 # cbind(copies0, copies_og1 = copies0$copies_mL) %>%
  select(Sample, Cq, Cq_og) %>%
  rename("Cq_redo" = "Cq")
